LC-MS ^13^C Lactate Measurements

### 2022-12-21 analysis/glc6-lactate.qmd
fix integration of GLC6 data into final flux measurements

```{r}
#| label: setup

@@

withr::with_dir(here::here(), {
  se_raw <- tar_read(fluxes_glc6_se)
  df_drift <- tar_read(fluxes_glc6_drift)
  std <- tar_read(conc_std)
})
```

@@

```{r}
#| label: raw-data
# df <-
#   read_ms_excel(here::here(path)) |> 
#   dplyr::filter(!str_detect(.data$id, "B")) |> 
#   tidyr::separate(
#     .data$sample, 
#     c("type", "number"), 
#     sep = "(?<=[[:alpha:]])(?=[[:digit:]])", 
#     fill = "left", 
#     convert = TRUE
#   ) |>
#   dplyr::mutate(
#     conc = ifelse(is.na(.data$type), .data$number, NA_character_), 
#     date = dplyr::case_when(
#       .data$type == "A" ~ "2022-11-12", 
#       .data$type == "B" ~ "2022-11-17", 
#       .data$type == "C" ~ "2022-11-22"
#     ), 
#     number = ifelse(!is.na(conc), NA, .data$number), 
#     batch = "b", 
#     cell_type = "lf", 
#     experiment = "substrate", 
#     type = dplyr::case_when(
#       .data$type == "QC" ~ "qc", 
#       is.na(.data$type) ~ "std", 
#       TRUE ~ "sample"
#     ), 
#     detector = "lcms", 
#     run = "a"
#   ) |> 
#   dplyr::select(
#     "metabolite", 
#     "detector", 
#     "mz", 
#     "rt", 
#     "cell_type",
#     "experiment", 
#     "batch", 
#     "date", 
#     "run", 
#     "id", 
#     "type", 
#     "number", 
#     "conc", 
#     "area"
#   )
```

## Drift

@@

```{r}
#| label: standard-curves

@@

pheno <- 
  tibble::tibble(
    number = 1:24, 
    oxygen = rep(c("21%", "0.5%"), times = 4, each = 3), 
    time = rep(c(0, 24, 48, 72), each = 6), 
    rep = rep(c("x", "y", "z"), 8)
  )

df_drift |> 
  filter(type %in% letters[1:3]) |> 
  filter(metabolite == "LAC M0") |> 
  left_join(pheno, by = "number") |> 
  group_by(type, oxygen, time) |> 
  wmo::remove_nested_outliers(area, remove = TRUE) |> 
  summarize(area = mean(area)) |> 
  ggplot() +
  aes(
    x = time, 
    y = area, 
    color = oxygen
  ) +
  geom_point() +
  stat_summary(
    geom = "line"
  )
```

>>>>

```{r}
#| label: setup
#| output: false

@@

withr::with_dir(here::here(), {
  se_raw <- tar_read(fluxes_glc6_se)
  df_drift <- tar_read(fluxes_glc6_drift)
  std <- tar_read(conc_std)
  fluxes <- tar_read(fluxes)
})
```

@@

## Drift Correction

@@

```{r}
#| label: standard-curves
#| results: hide

@@

fluxes |> 
  filter(experiment == "substrate")
df_drift |> 
  filter(type %in% letters[1:3]) |> 
  filter(metabolite == "LAC M0") |> 
  left_join(pheno, by = "number") |> 
  group_by(type, oxygen, time) |> 
  wmo::remove_nested_outliers(area, remove = TRUE) |> 
  summarize(area = mean(area)) |> 
  ggplot() +
  aes(
    x = time, 
    y = area, 
    color = oxygen
  ) +
  geom_point() +
  stat_summary(
    geom = "line"
  )
```
